R Notebook

### 2021-10-29 FEM_R/Wealth_Health_Socioeconomics.Rmd
Hotdecked some variables to make both the repl_standard and repl_modified_quint1 populations run through simulation. Can now start assessing the outcome of the intervention

@@

@@

```{r}
## REMEMBER ACCOUNTING! SMOKING VARS AND EXSTAT

# which variables to select and impute
# Need to do this in parts because some of the lags wouldn't impute when 
# the current vars were included. Specifically smoken, smokev, and problem_drinker
demog.vars <- c('idauniq', 'wealth_quint', 'age', 'male')
risk.vars.fir <- c('smokev', 'smoken', 'heavy_smoker', 'drink', 
                   'problem_drinker', 'logbmi',  'exstat', 'l2drink', 
                   'l2logbmi', 'l2exstat')
risk.vars.sec <- c('heavy_smoker', 'drink', 'logbmi',  'exstat', 'l2smoken',
                   'l2smokev', 'l2heavy_smoker', 'l2drink', 'l2problem_drinker',
                   'l2logbmi', 'l2exstat')

## Have a go at multiple imputation using distribution from median quintile first
# First generate a test dataset with only the variables we need to impute and age,sex
test.fir <- repl %>% filter(year == 2012, wealth_quint %in% c(1, 3)) %>%
                  select(all_of(demog.vars), all_of(risk.vars.fir))

test.sec <- repl %>% filter(year == 2012, wealth_quint %in% c(1, 3)) %>%
                  select(all_of(demog.vars), all_of(risk.vars.sec))

# Remove data for the risk behaviours for wealth_quint == 1
# Doing this in chunks as not sure of a better way
#test.1 <- test[test$wealth_quint == 1]
#test.3 <- test[test$wealth_quint == 3]

test.1.fir <- filter(test.fir, wealth_quint == 1)
test.1.sec <- filter(test.sec, wealth_quint == 1)
test.3.fir <- filter(test.fir, wealth_quint == 3)
test.3.sec <- filter(test.sec, wealth_quint == 3)

# replace all risk var information with NA for lowest quintile
test.1.fir[risk.vars.fir] <- NA
test.1.sec[risk.vars.sec] <- NA

# Now put them all back together with a rbind
test.fir <- rbind(test.1.fir, test.3.fir)
test.sec <- rbind(test.1.sec, test.3.sec)

# Now have a go at imputing all missings
imp <- mice(data=test.fir, m=5, maxit=10, printFlag = FALSE)

# get a complete version of the dataset
test2.fir <- complete(imp)

imp2 <- mice(data=test.sec, m=5, maxit=10, printFlag = FALSE)

test2.sec <- complete(imp2)

test2 <- merge(test2.fir, test2.sec, by = 'idauniq')

rm(test.1.fir, test.1.sec, test.3.fir, test.3.sec, risk.vars.fir, risk.vars.sec,
   test.fir, test.sec)
```

id.var <- 'idauniq'
demog.vars <- c('wealth_quint', 'age', 'male')
risk.vars <- c('smokev', 'l2smokev', 'smoken', 'l2smoken', 'heavy_smoker',
               'l2heavy_smoker', 'drink', 'l2drink', 'problem_drinker',
               'l2problem_drinker', 'logbmi', 'l2logbmi', 'exstat',
               'l2exstat')

#test.1 <- test[test$wealth_quint == 1]
#test.3 <- test[test$wealth_quint == 3]

test.1 <- test %>% filter(wealth_quint == 1)
test.3 <- test %>% filter(wealth_quint == 3)

test.1[risk.vars] <- NA

test <- rbind(test.1, test.3)

imp <- mice(data=test, m=5, maxit=10, printFlag = FALSE)

# get a complete version of the dataset
test2 <- complete(imp)

### ACCOUNTING
# if smoken == 1 then most likely l2smoken == 1 also
# if (is.na(test2$l2smoken)) {
#   test2$l2smoken <- test2$smoken
# }
test2$l2smoken[is.na(test2$l2smoken)] <- test2$smoken

# if l2smokev == 1 then smokev must also == 1
# if (is.na(test2$smokev)) {
#   test2$smokev <- test2$l2smokev
#   # also, if l2smoken == 1 then l2smokev must also equal 1
#   if (test2$l2smoken == 1) {
#     test2$l2smokev <- 1
#   }
#   # same for smoken
#   if (test2$smoken == 1)
#     test2$l2smoken <- 1
# }
test2$smokev[is.na(test2$smokev)] <- test2$l2smokev
test2$l2smokev[test2$l2smoken == 1] <- 1
test2$l2smoken[test2$smoken == 1] <- 1

# no variability in problem_drinker -> l2problem_drinker in median wealth group,
# so assume same here
# if (is.na(test2$l2problem_drinker)) {
#   test2$l2problem_drinker <- test2$problem_drinker
# }
test2$l2problem_drinker[is.na(test2$l2problem_drinker)] <- test2$problem_drinker

```{r}
## Step 2 is now to replace the values from the original repl dataset and save 
# this as an alternative for running through the model

table(repl.final2$educl)
summary(repl.final2$educl)
print('---------')

## USE THIS SPACE TO HOTDECK LOTS OF MISSING VARIABLES (start with lnly)
```

>>>>

# for hotdecking
require(VIM)

@@

```{r}
# Set up lists of id vars, demographic vars (for imputation) and risk vars to be imputed
id.var <- 'idauniq'
demog.vars <- c('wealth_quint', 'age', 'male')
risk.vars <- c('smokev', 'l2smokev', 'smoken', 'l2smoken', 'heavy_smoker',
               'l2heavy_smoker', 'drink', 'l2drink', 'problem_drinker',
               'l2problem_drinker', 'logbmi', 'l2logbmi', 'exstat',
               'l2exstat')

# separate test df by quintile so we can remove data for quint1
test.1 <- test %>% filter(wealth_quint == 1)
test.3 <- test %>% filter(wealth_quint == 3)
test.1[risk.vars] <- NA
test <- rbind(test.1, test.3)

# Run mi & get a complete version of the imputed dataset
imp <- mice(data=test, m=5, maxit=10, printFlag = FALSE)
test2 <- complete(imp)

### ACCOUNTING
# if smoken == 1 then most likely l2smoken == 1 also
test2$l2smoken[is.na(test2$l2smoken)] <- test2$smoken

# if l2smokev == 1 then smokev must also == 1
test2$smokev[is.na(test2$smokev)] <- test2$l2smokev
# also, if l2smoken == 1 then l2smokev must also equal 1
test2$l2smokev[test2$l2smoken == 1] <- 1
# same for smoken
test2$l2smoken[test2$smoken == 1] <- 1

# no variability in problem_drinker -> l2problem_drinker in median wealth group,
# so assume same here
test2$l2problem_drinker[is.na(test2$l2problem_drinker)] <- test2$problem_drinker

```{r}
## Next step is to replace the values from the original repl dataset and save 
# this as an alternative for running through the model

#table(repl.final2$educl)
#summary(repl.final2$educl)
#print('---------')

## USE THIS SPACE TO HOTDECK LOTS OF MISSING VARIABLES (start with lnly)
hotdeck.vars <- c('lnly', 'workstat', 'smokev')

repl.final2 <- hotdeck(repl.final2, variable = hotdeck.vars)
repl2 <- hotdeck(repl2, variable = hotdeck.vars)
```

# Output Visualisation

@@
